Algebraic filtering of surfaces from medical images with Julia

### 2020-04-17 src/paper.tex
new square magenta image
Updates from Overleaf

%TODO fix the name
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=0.4\linewidth]{figs/grid.pdf} 
   \caption{example caption}
   \label{fig:example}
\end{figure}

@@

\item remove both instances of \emph{double quads} generated by \texttt{Lar} software at the block boundaries (see Figure~\ref{fig:blockboundary}). They are artifacts generated by the decomposition of the whole image into a number of blocks of tractable size.

\item 
a smart strategy of removal of such artifacts may be used, which does not require any sorting nor searching on the assembled array of quads. It will consist in arranging each block with all three dimensions decreased-increased by one, so that each 2-adjacent pair of blocks will be covering each other for a full side extent of blocks of depth one. The details of this \emph{artifact filtering} are elucidated in Section~\ref{sec:covering}.

@@

\subsubsection*{Smoothing}\label{sec:smoothing}
The final smoothing of the generated surfaces cannot be performed block-wise, since this would introduce smoothing artifacts at the block boundaries. Anyway, the Taubin smoothing~\cite{} can be performed in parallel, since for each vertex in the final surface (except eventually the ones on the image $\mathcal{I}$ boundaries) it essentially consist in computing a new position as a proper average of its neighborhood vertices, i.e.~by applying a discrete Laplacian operator.  Some appropriate set of workers may so be assigned the task of generating iteratively a new position for the vertices they take cure of. In particular, we have:
\begin{enumerate}

@@

% \includegraphics[height=0.3\textwidth]{figs/nrn10_100_green.png} 
%\includegraphics[scale=1]{input/ircad_comparison.pdf} 
\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{figs/liver_01_red_3.png} 
% \vspace{0.05\textwidth}
\includegraphics[width=0.4\textwidth]{figs/portalvein_01_yellow_3.png} 
% \vspace{0.01\textwidth}
\includegraphics[height=0.4\textwidth]{figs/nrn10_100_low_res.png} 
% \vspace{0.05\textwidth}
\includegraphics[width=0.4\textwidth]{figs/porta_smoothing_2.png} 
\caption{
Triangulated isosurface of liver parts extracted with LAR-SURF algorithm. 
On the upper left image the surface of the liver parenchyma of human can be seen. 
Both right images show the Portal Vein from the same Ircad dataset \cite{ircad} 
with resolution $1.6\times0.57\times0.57$ [mm].
On the left bottom image is the pig liver microvasculature based on corrosion cast prepared by Eberlova
\cite{eberlova2017use}. The resolution of the Micro-CT data is 4.682 $\mu{}m$.
} \label{fig:example_liver_macro_micro}
\end{figure}

>>>>

% TODO fix the name
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=0.4\linewidth]{figs/grid.pdf} 
   \caption{example caption}
   \label{fig:example}
\end{figure}

@@

\item remove both instances of \emph{double quads} generated by \texttt{Lar} software at the block boundaries 
(see Figure~\ref{fig:blockboundary}). 
% TODO fix reference probably uncomment next line to link it to Figure 3
% (see Figure~\ref{fig:example}). 
They are artifacts generated by the decomposition of the whole image into a number of blocks of tractable size.

\item 
a smart strategy of removal of such artifacts may be used, which does not require any sorting nor searching on the assembled array of quads. It will consist in arranging each block with all three dimensions decreased-increased by one, so that each 2-adjacent pair of blocks will be covering each other for a full side extent of blocks of depth one. The details of this \emph{artifact filtering} are elucidated in Section~\ref{sec:covering}.
% TODO fix the reference

@@

\subsubsection*{Smoothing}\label{sec:smoothing}
The final smoothing of the generated surfaces cannot be performed block-wise, since this would introduce smoothing artifacts at the block boundaries. Anyway, the Taubin smoothing~\cite{Taubin1995} can be performed in parallel, since for each vertex in the final surface (except eventually the ones on the image $\mathcal{I}$ boundaries) it essentially consist in computing a new position as a proper average of its neighborhood vertices, i.e.~by applying a discrete Laplacian operator.  Some appropriate set of workers may so be assigned the task of generating iteratively a new position for the vertices they take cure of. In particular, we have:
\begin{enumerate}

@@

% \includegraphics[height=0.3\textwidth]{figs/nrn10_100_green.png} 
%\includegraphics[scale=1]{input/ircad_comparison.pdf} 
\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{figs/liver_01_red_3.png} 
% \vspace{0.05\textwidth}
\includegraphics[width=0.4\textwidth]{figs/portalvein_01_yellow_3.png} 
% \vspace{0.01\textwidth}
\includegraphics[height=0.4\textwidth]{src/figs/nrn10_100_magenta_high_res.png} 
% \includegraphics[height=0.4\textwidth]{figs/nrn10_100_low_res.png} 
% \vspace{0.05\textwidth}
\includegraphics[width=0.4\textwidth]{figs/porta_smoothing_2.png} 
\caption{
Triangulated isosurface of liver parts extracted with LAR-SURF algorithm. 
On the upper left image the surface of the liver parenchyma of human can be seen. 
Both right images show the Portal Vein from the same Ircad dataset \cite{ircad} 
with resolution $1.6\times0.57\times0.57$ [mm].
On the left bottom image is the pig liver microvasculature based on corrosion cast prepared by Eberlova
\cite{eberlova2017use}. The resolution of the Micro-CT data is 4.682 $\mu{}m$.
} \label{fig:example_liver_macro_micro}
\end{figure}
